Continuous Deductive Reasoning over Streamed RDF Data

### 2015-07-01 content/personal-details-els.tex
changed title to final
Removed middle initial
set myself as the corresponding author
Fixed personal details

% Personal Details
\begin{frontmatter}
	\title{Something about Continuous Deductive Reasoning over Streamed RDF Data, maybe claim Soundness or some other Theoretical Quality}

	\author{David L. Monks}
	\ead{dm11g08@ecs.soton.ac.uk}
	\author{Rehab Albeladi}
	\ead{raab1g09@ecs.soton.ac.uk}
	\author{Nicholas M. Gibbins}
	\ead{nmg@ecs.soton.ac.uk}
	% \ead{\{dm11g08,raab1g09,nmg\}@ecs.soton.ac.uk}
	\address{
	          Department of Electronics and Computer Science,\\
	          Faculty of Physical Sciences and Engineering,\\
	          University of Southampton,\\
	          University Rd., Southampton, SO17 1BJ,\\
	          United Kingdom
	}
	% TODO fix Rehab's details

>>>>

% Personal Details
\begin{frontmatter}
	\title{Continuous Deductive Reasoning over Streamed RDF Data}

	\author{David L. Monks}
	\ead{dm11g08@ecs.soton.ac.uk}
	\author{Rehab Albeladi}
	\ead{raab1g09@ecs.soton.ac.uk}
	\author{Nicholas Gibbins}
	\ead{nmg@ecs.soton.ac.uk}
	% \ead{\{dm11g08,raab1g09,nmg\}@ecs.soton.ac.uk}
	\address{
	          Electronics and Computer Science,\\
	          University of Southampton,\\
	          Southampton, SO17 1BJ,\\
	          United Kingdom
	}
	% TODO fix Rehab's details
